### 2025-04-14 MetadataS1/MetadataS1.tex
minor changes from reviewers comments

        \subsection*{2. Experimental or sampling design}

@@

\newpage
\subsubsection*{c. Observation of individuals}
\begin{enumerate}[label=\roman*]
\item[] \textit{\textbf{Vertebrate count transects}}\\
From 2010 to 2023, observers walked 500-meter linear transects where all vertebrate individuals observed within 150 meters on either side were counted (146 to 320 transects per year). Transects were distributed across all lowland zones of the study area, typically in mesic habitat, and were carried out during the nesting period (between June 21 and July 14; \citet{duchesne2021}; \textbf{Figure \ref{figure:transects}}). Furthermore, specifically for American golden-plovers, we measured the distance of each observed individual to the transect path.
\\
\begin{figure}
\centering
  \includegraphics[width=0.7\textwidth, angle=0]{figures/transects.pdf}
  \vspace{-35pt} % Reduce space between figure and caption
  \caption{Spatial distribution of vertebrate count transects (white lines) on the south plain of Bylot Island (146 to 320 transects per year).}
 \label{figure:transects}
\end{figure}
\newpage
\item[] \textit{\textbf{Snow goose point count}}\\
At the start, middle, and end of each vertebrate count transect, a point count with a radius of 125 meters was conducted to determine the number of snow goose breeding pairs. On average, 613 \textpm{142} point counts were sampled each year, covering an area of 30 \textpm{7} km\textsuperscript{2}.
\\
\item[] \textit{\textbf{Incidental observations}}\\
Since 2007, observers have recorded all vertebrate species observed opportunistically during field work and tallied the total number of individuals at the end of each day \citep{gauthier2020daily, gauthier2024a}. The number of hours spent in the field served as a proxy for the sampling effort. We used the number of individuals observed per hour spent in the field calculated by \citet{gauthier2024a} as an index of relative abundance for each species. Moreover, we separated observations made in lowland from those in upland zones to have a relative abundance of each species in each of these two broad categories (\textbf{Table \ref{table:table_species_relative_abundance_upland}}). Given that incidental observations lacked georeferencing, we opted to extract upland observations by focusing on observations made during visits to rough-legged hawk nests, which are mostly located in uplands. \\
\input{tables/table_species_relative_abundance_upland.tex}
%label-> table_species_relative_abundance_upland
\newpage
\item[] \textit{\textbf{Testimonials of ermine sightings}}\\
There was no direct estimation of ermine abundance on Bylot Island as they are quite difficult to obtain. The density estimates for ermine were derived from an annual abundance index established by \citet{bolduc2023}, which relied on testimonials provided by observers across the whole study area from 1993 to 2019. The testimonials provided by observers were used to create an abundance index ranging from 0 to 3 \citep{bolduc2023}. In this index, a score of 0 corresponds to the absence of ermine sightings, 1 indicates a single sighting of a lone individual, 2 represents multiple sightings of lone individuals, and 3 signifies at least one sighting of a family group. Scores of individual participants were averaged annually as detailed in \citet{bolduc2023}.

>>>>

        \subsection*{2. Experimental or sampling design}
Research installations on Bylot Island are typically active from mid-May to the 20th of August due to logistical constraints. The period therefore covers the arrival of migratory species and the entire breeding cycle for most species. However, the sampling period does not encompasses the departure of some species (e.g., xxxxx).

@@

\newpage
\subsubsection*{c. Observation of individuals}
\begin{enumerate}[label=\roman*]
\item[] \textit{\textbf{Vertebrate count transects}}\\
From 2010 to 2023, observers walked 500-meter linear transects where all vertebrate individuals observed within 150 meters on either side were counted (146 to 320 transects per year). Transects were distributed across all lowland zones of the study area, typically in mesic habitat, and were carried out during the nesting period (between June 21 and July 14; \citet{lamarre2017, duchesne2021}; \textbf{Figure \ref{figure:transects}}). As a calibration, all observers were trained with a rangefinder to estimate a distance of 150 m before starting data collection. Furthermore, specifically for American golden-plovers, we measured the distance of each observed individual to the transect path.
\\
\begin{figure}
\centering
  \includegraphics[width=0.7\textwidth, angle=0]{figures/transects.pdf}
  \vspace{-35pt} % Reduce space between figure and caption
  \caption{Spatial distribution of vertebrate count transects (white lines) on the south plain of Bylot Island (146 to 320 transects per year).}
 \label{figure:transects}
\end{figure}
\newpage
\item[] \textit{\textbf{Snow goose point count}}\\
At the start, middle, and end of each vertebrate count transect, a point count with a radius of 125 meters was conducted to determine the number of snow goose breeding pairs. On average, 613 \textpm{142} point counts were sampled each year, covering an area of 30 \textpm{7} km\textsuperscript{2}. Observers were trained with a rangefinder to estimate a distance of 125 m before starting data collection.
\\
\item[] \textit{\textbf{Incidental observations}}\\
Since 2007, observers have recorded all vertebrate species observed opportunistically during field work and tallied the total number of individuals at the end of each day \citep{gauthier2020daily, gauthier2024a}. Observations are made from mid-May to the late August, but the effort is highest during the late June and early July. The number of hours spent in the field served as a proxy for the sampling effort. We used the number of individuals observed per hour spent in the field calculated by \citet{gauthier2024a} as an index of relative abundance for each species. Moreover, we separated observations made in lowland from those in upland zones to have a relative abundance of each species in each of these two broad categories (\textbf{Table \ref{table:table_species_relative_abundance_upland}}). Given that incidental observations lacked georeferencing, we opted to extract upland observations by focusing on observations made during visits to rough-legged hawk nests, which are mostly located in uplands. \\
\input{tables/table_species_relative_abundance_upland.tex}
%label-> table_species_relative_abundance_upland
\newpage
\item[] \textit{\textbf{Testimonials of ermine sightings}}\\
There was no direct estimation of ermine abundance on Bylot Island as they are quite difficult to obtain. The density estimates for ermine were derived from an annual abundance index established by \citet{bolduc2023}, which relied on testimonials provided by observers across the whole study area from 1993 to 2019. The testimonials provided by observers were used to create an abundance index ranging from 0 to 3 \citep{bolduc2023}. In this index, a score of 0 corresponds to the absence of ermine sightings, 1 indicates a single sighting of a lone individual, 2 represents multiple sightings of lone individuals, and 3 signifies at least one sighting of a family group. Scores of individual participants were averaged annually as detailed in \citet{bolduc2023}.
